---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

# quantarcticR

Quantarctica is a collection of Antarctic geographical datasets which works with the free, cross-platform, open-source software QGIS. It includes community-contributed, peer-reviewed data from ten different scientific themes and a professionally-designed basemap. This package provides access to Quantarctica data sets for R users, who can use these data sets with e.g. the `raster`, `sp`, or `sf` packages.

## Installation

You can install the development version of quantarcticR from GitHub with:

```{r eval = FALSE}
remotes::install_github("SCAR-sandpit/quantarcticR")
```

This is very much a work in progress!

## Example

```{r example}
library(quantarcticR)
```


List all available datasets:

```{r example2}
ds <- qa_datasets()
head(ds)
```

Fetch one and plot it:

```{r example3}
res <- qa_get("ADD Simple basemap", verbose = TRUE)

library(raster)
x <- shapefile(res$main_file)
plot(x)
```

