---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  warning = FALSE,
  message = FALSE,
  out.width = "100%"
)
library(quantarcticR)
## for vignette purposes, and if this is Ben's computer, use a persistent cache_dir
if (grepl("ben_ray", qa_cache_dir())) qa_cache_dir("c:/data/Quantarctica3")
```

[![Travis build status](https://travis-ci.org/SCAR-sandpit/quantarcticR.svg?branch=master)](https://travis-ci.org/SCAR-sandpit/quantarcticR)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/SCAR-sandpit/quantarcticR?branch=master&svg=true)](https://ci.appveyor.com/project/SCAR-sandpit/quantarcticR)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Coverage status](https://codecov.io/gh/SCAR-sandpit/quantarcticR/branch/master/graph/badge.svg)](https://codecov.io/github/SCAR-sandpit/quantarcticR?branch=master)

# quantarcticR

Quantarctica is a collection of Antarctic geographical datasets which works with the free, cross-platform, open-source software QGIS. It includes community-contributed, peer-reviewed data from ten different scientific themes and a professionally-designed basemap.

The `quantarcticR` package provides access to Quantarctica data sets for R users, **without** needing QGIS to be installed. R users can use these data sets with e.g. the `raster`, `sp`, or `sf` packages.

## Installation

You can install the development version of quantarcticR from GitHub with:

```{r eval = FALSE}
remotes::install_github("SCAR-sandpit/quantarcticR")
```

This is very much a work in progress!

## Example
```{r example}
library(quantarcticR)
```


List all available datasets:

```{r example2}
ds <- qa_datasets()
head(ds)
```

Fetch one and plot it:

```{r example3}
res <- qa_get("ADD Simple basemap", verbose = TRUE)

library(raster)
plot(res)
```

See the [introductory vignette](https://scar-sandpit.github.io/quantarcticR/articles/intro.html) for more information.

## See also

[RQGIS](https://cran.r-project.org/package=RQGIS) provides an R-QGIS interface, via Python middleware.
