---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  warning = FALSE,
  message = FALSE,
  out.width = "100%"
)
library(quantarcticR)
## for vignette purposes, and if this is Ben's computer, use a persistent cache_dir
if (grepl("ben_ray", qa_cache_dir())) qa_cache_dir("c:/data/Quantarctica3")
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/SCAR/quantarcticR/workflows/R-CMD-check/badge.svg)](https://github.com/SCAR/quantarcticR/actions)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Codecov test coverage](https://codecov.io/gh/SCAR/quantarcticR/branch/master/graph/badge.svg)](https://codecov.io/gh/SCAR/quantarcticR?branch=master)
<!-- badges: end -->

# quantarcticR

Quantarctica is a collection of Antarctic geographical datasets which works with the free, cross-platform, open-source software QGIS. It includes community-contributed, peer-reviewed data from ten different scientific themes and a professionally-designed basemap.

The `quantarcticR` package provides access to Quantarctica data sets for R users, **without** needing QGIS to be installed. R users can use these data sets with e.g. the `raster`, `sp`, or `sf` packages.

## Installation

You can install the development version of quantarcticR from GitHub with:

```{r eval = FALSE}
remotes::install_github("SCAR/quantarcticR")
```

## Example
```{r example}
library(quantarcticR)
```

`quantarcticR` will download data from whichever Quantarctica mirror has been selected. The USA mirror is chosen by default, but you can change this: see `help("qa_mirror")`.

List all available datasets:

```{r example2}
ds <- qa_datasets()
head(ds)
```

Fetch one and plot it:

```{r example3}
res <- qa_get("ADD Simple basemap", verbose = TRUE)

library(raster)
plot(res)
```

See the [introductory vignette](https://scar.github.io/quantarcticR/articles/intro.html) for more information.

## See also

[qgisprocess](https://CRAN.R-project.org/package=qgisprocess)
[RQGIS](https://github.com/r-spatial/RQGIS) ARCHIVED: provides an R-QGIS interface, via Python middleware.
