---
title: "1. Intro quantarticR"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{1. Intro quantarticR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

The `quantarcticR` package provides access to Quantarctica data sets for R users, **without** needing QGIS to be installed. 

This vignette:

* explains what Quantarctica data is
* shows how the datasets can be used in R 
* provides examples of how you can work with them


# What is Quantarctica?

[Quantarctica](http://quantarctica.npolar.no/about.html) is a collection of Antarctic geographical datasets which works with the free, cross-platform, open-source software QGIS. It includes community-contributed, peer-reviewed data from ten different scientific themes and a professionally-designed basemap.

Quantarctica is is published and made available under [under a Creative Commons Attribution 4.0 International License](https://creativecommons.org/licenses/by/4.0/).

If you use a `dataset`, please cite it:  

Matsuoka K, Skoglund A, Roth G (2018) Quantarctica `dataset`. Norwegian Polar Institute.
https://doi.org/10.21334/npolar.2018.8516e961

# Caching datasets

The [quantarcticR](https://github.com/SCAR-sandpit/quantarcticR) R package provides you with flexibility to either temporarily or persistently store the data.

On loading the package, you will be provided with two options:  

1: Yes. Use a temporary cache directory for this session only  
2: No. Use the persistent cache directory

.... Can you change to the other option after you have loaded the package?....

... May need some add when to use which option ...

# Quantarctica Data Sets

```{r}
library(quantarcticR)
```

In order to return a list of the datasets available, use the `qa_datasets` function.

```{r}
datasets <- qa_datasets()
class(datasets)
```

The list is of class `r class(datasets)` which can also be used with tidyverse functions.

```{r}
head(datasets)
```

In the `datasets` object we can see the following:  

- `layername` which is the name of the dataset  
- `type` which is the object type shapefile or raster
- `cache` whether cached or not  
- `download_size` which is the size of the `layername` dataset

# Dataset details

In order to view the details of a dataset use the `qa_dataset` function for the simple basemap called "ADD Simple basemap".

```{r}
dataset <- qa_dataset("ADD Simple basemap")
class(dataset)
```

.... is there a print or summary function for the qa_dataset object?....

# Fetch a dataset

To fetch a dataset use the `qa_get` function with the dataset `layername`.

First fetch the simple basemap called "ADD Simple basemap".

```{r}
#basemap <- qa_get("ADD Simple basemap", verbose = TRUE)
#class(basemap)
```


```{r}
gravity_anomaly <- qa_get("AntGG Free-air gravity anomaly (10km)", verbose = TRUE)
class(gravity_anomaly)
```

This returns a object of class `r class(gravity_anomaly)`.

# Raster Plot 

Use the Raster package to plot these two objects.

```{r, error=FALSE, message=FALSE}
library(raster)
#raster::plot(basemap)
```

```{r}
raster::plot(gravity_anomaly)
```

# Using datasets with sf

Read in the data as an sf object and use the ggplot2 and sf packages to create a plot.

```{r}
library(sf)
library(ggplot2)

surface_sf <- qa_get("ADD Simple basemap", shapefile_reader = sf::st_read)

surface_sf
class(surface_sf)
surface_sf %>% 
  ggplot() +
  geom_sf()
```

